Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-04 ms.tex
section 4 refixing

  {$\left(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\

@@

Our analytic estimates accurately reproduce the numerical results in
the high heating limit $\zeta \gg 1$ ($v_w \gg \sigma_0$; $r_{\rm s}
\lesssim r_{\rm soi}$).  However, for sufficiently low heating the
stagnation radius diverges above the analytic estimate, approaching
the stellar break radius $r_b \gg r_{\rm soi}$.  This divergence
occurs approximately when $\zeta < \zeta_c \propto (r_b/r_{\rm
  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which in Appendix
\ref{app:be} is shown to coincide with the critical heating below which the Bernoulli parameter of the gas decreases below unity near the stagnation radius.  This divergence of the stagnation radius to large radii hence occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.8$) with large break radii.  This dependence explains the behavior of the two core galaxies, shown as
orange triangles vertically aligned at the same value of
$\zeta$. These correspond to models with the same black hole mass
($\Mbh = 10^8 \Msun$) and heating rate ($v_w = 600$ km s$^{-1}$) but
different values of the break radius: $r_{b} =$ 25, 50 pc (from top to
bottom). {\bf AG still needs work.  BDM: what work? this looks sufficient to me}

@@

In addition to our standard set of solutions neglecting thermal conduction and cooling, we explore a few test simulations including these effects, as marked by dagger symbols in Table \ref{table:models}.  For solutions which are far from being thermally unstable when cooling is neglected (e.g. $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the effects of including radiative cooling on the key properties of the flow (stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ ratio) are small.  However, for solutions in which cooling stability is marginal (e.g. $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim $few), including cooling decreases the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fraction.  In particular, we ran solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and all cores with $v_w=600 $ km s$^{-1}$, each for three different values of the mass input parameter spanning the physically expected range $\eta = 0.02,
0.2, 0.6$.  Solutions which are found to be unstable for all values of $\eta$ are marked with a $\mathbf{TI}$ in Table \ref{table:models}.

>>>>

  {$\left(\frac{\dot{q}_{\rm heat}}{|\dot{q}_{\rm rad}|}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$} & Issues? \\

@@

Our analytic estimates accurately reproduce the numerical results in
the high heating limit $\zeta \gg 1$ ($v_w \gg \sigma_0$; $r_{\rm s}
\lesssim r_{\rm soi}$).  However, for sufficiently low heating the
stagnation radius diverges above the analytic estimate, approaching
the stellar break radius $r_b \gg r_{\rm soi}$.  This divergence
occurs approximately when $\zeta < \zeta_c \propto (r_b/r_{\rm
  soi})^{0.5(\Gamma-1)}$ (eq.~[\ref{eq:zetacrit}]), which in Appendix
\ref{app:be} is shown to coincide with the Bernoulli parameter of the gas decreasing below unity near the stagnation radius.  This divergence of the stagnation radius to large radii hence occurs at a higher value of $\zeta$ in core galaxies ($\Gamma = 0.8$) with large break radii.  This dependence explains the behavior of the two core galaxies, shown as
orange triangles vertically aligned at the same value of
$\zeta$. These correspond to models with the same black hole mass
($\Mbh = 10^8 \Msun$) and heating rate ($v_w = 600$ km s$^{-1}$) but
different values of the break radius: $r_{b} =$ 25, 50 pc (from top to
bottom). {\bf AG still needs work.  BDM: what work? this looks sufficient to me}

@@

In addition to our standard set of solutions neglecting thermal conduction and cooling, we explore a few test simulations including these effects, as marked by dagger symbols in Table \ref{table:models}.  For solutions which are far from being thermally unstable when cooling is neglected (e.g. $M_{\bullet} = 10^{8}M_{\odot}$, $v_{w} = 600$ km s$^{-1}$, $r_{b} = 100$ pc, $\eta = 0.2$, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| = 76$), the effects of including radiative cooling on the key properties of the flow (stagnation radius, mass accretion rate, $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ ratio) are small.  However, for solutions in which cooling stability is marginal (e.g. $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}| \sim $few), including cooling decreases the value of $\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ by a greater fraction.  In particular, we ran solutions with radiative cooling for all cusp galaxies with $v_w=300$ km s$^{-1}$ and all core galaxies with $v_w=600 $ km s$^{-1}$, each for three different values of the mass input parameter $\eta = 0.02,
0.2, 0.6$, spanning the physical range.  Solutions found to be unstable for all values of $\eta$ are marked with a $\mathbf{TI}$ in Table \ref{table:models}.
